Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-06 paper-v1.tex
editorial process source

\section{Background}
\subsection{Peer-review: a flawed and outdated system}
Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination. However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times. 
\subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications. 
\paragraph{Traditional peer-review process}
\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria. If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers. Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability. They then accept or decline. If they decline, they might suggest alternative reviewers. Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves. 
    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process. 
    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.

@@

\subsection{Implementation}
\subsubsection{Back-end} ??
AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

@@

\subsubsection{Bounty}
AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
\newline It implements a Bounty-like system where an issuer (author) is asked a serious of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
  \item to speficy a deadline in the form of a unix timestamp after wich the fulfillment will no longer be accepted.
  \item to send the amount of ether for the reward.
\end{itemize}

@@

\subsubsection{Token Economics} what is this?

>>>>

\section{Background}
\subsection{Peer-review: a flawed and outdated system}
Peer-review is the traditional and necessary process at the heart of quality control in science [9, 12], determining the destinies of articles’ publications and therefore of scientific dissemination. However, the current peer-review system is outdated: in the past, it was effective when scholarly communication happened exclusively through printed paper journals, but nowadays, with the high and fast-paced levels of articles productions, its slow and multistage process doesn’t keep up with the times. 
\subsubsection{It's a slow multi-stage process.} Indeed, articles submitted to journals can take from months to years after editors’ first scrutiny, going back and forth several review rounds before acceptance for publications. 
\paragraph{Traditional peer-review process} This section takes inspiriration from the editorial processes at Nature Methods and Wiley.
\begin{enumerate}
    \item The author submits a manuscript to the journal.
    \item  An editorial team  assesses the paper for what concerns the requirements of the journal's Author's Guideline (composition, sections...).
    \item An Editor in Chief (EIC) is assigned to the manuscript and checks if the paper meets the scopes of the journal and novelty criteria. If the paper is rejected, it does not go through the consideration process and the editor notifies the author.
    \item If the editorial decision is to send the manuscript for review, the handling editor looks for potential reviewers. Potential reviewers can be suggested by the authors themselves, but usually it's up to the editor to find researchers in the field who are competent enough but not closely related to the study to review.
    \item Candidate reviewers receive the journal's invitation and evaluate acceptance based on their own level of expertise, intrinsic conﬂicts of interest and time availability. They then accept or decline. If they decline, they might suggest alternative reviewers. Editors keep searching for reviewers until they find two or three reviewers who agree to review the manuscript.
    \item When reviewers engage themselves in delivering peer-review report by a certain deadline, the author(s) are notified. The reviewers identity is usually only know to the editor but is hidden to the authors or the other reviewers themselves. 
    \item Reviewers independently conduct their reviews by exposing in their reports strengths and weaknesses of the manuscript in a point-by-point fashion and submitting a final recommendation to the editor: acceptance, rejection or revision (major or minor).
    \item the handling editor or the editorial team considers all the submitted reports and makes the final decision.
    \item If the decision is a major or minor revision, authors are invited to re-submit a corrected or improved version of the manuscript with a letter to the reviewers. The same reviewers might be contacted again and if they want they can follow up the peer-review process. 
    \item If the decision is a rejection, the editor might indicate another journal where to submit the manuscript.

@@

\subsection{Implementation}
\subsubsection{Back-end} ?? BETTER HERE SAY WHAT WE HAVE ALREADY DONE, PRESENTED 
AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

@@

\subsubsection{Token economy and Bounty}
AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
\newline It implements a Bounty-like system where an issuer (author) is asked a serious of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
  \item to speficy a deadline in the form of a unix timestamp after wich the fulfillment will no longer be accepted.
  \item to send the amount of ether for the reward.
\end{itemize}

@@
